Computational hysteresis:\\ inter-task effects in human computation

### 2014-11-06 docs/publications/2014.09_SCIENCE/man.tex
add self-specificity analysis and crawler

\begin{mydef}
	\label{def:bias}
	{\upshape Maximum Bias:}
	Let $\mathcal{D}$ be a binary decision function, which takes a 
	work-product
	$r \in P \cup Q$ as input, and outputs a bit $\mathcal{D}(r)=b$, where 
	$b \in \{0,1\}$. Denote the \emph{bias} of $\mathcal{D}$, due to the
	different priming of $\mathcal{P}$ and $\mathcal{Q}$ by
	$\theta_\mathcal{D}(P,Q)$ and define it to be the difference 
	in the expected output of $\mathcal{D}$ when acting on work-products from 
	$P$ and $Q$:
	$$
	\mathcal{D}(P,Q) = 
		\left| 
			\mathrm{E}\left\{ \mathcal{D}(p) \right\} 
			- \mathrm{E}\left\{ \mathcal{D}(q) \right\} 
		\right|,
	\theta_\mathcal{D}(P,Q) = 
		\left| 
			\mathrm{E}\left\{ \mathcal{D}(p) \right\} 
			- \mathrm{E}\left\{ \mathcal{D}(q) \right\} 
		\right|,
	$$
	where $p \in P$, $q \in Q$.  Then, define the difference in priming 
	between $\mathcal{P}$ and $\mathcal{Q}$ to be the worst-case bias, i.e. 
	the bias of the most susceptible decision:
	$$
	\theta(P,Q) = 
		\sup_\mathcal{D} \theta_\mathcal{D}(P,Q)
	$$
\end{mydef}
If $\mathcal{D}$ is the condition of an \texttt{if}-statement, then the 
definition above is the change in the fraction of the time that a given 
path of execution is followed due to HPU priming.

@@

\paragraph{Sufficiency of framing.} Given just how much stronger
inter-task effects were, the reader may wonder whether the framing was 
in some sense ``sufficient''.  
We designed our framing tasks based on
work that had previously studied framing effects in micro-task settings.  
Prior studies have shown that framing the purpose of a task, or indeed, 
simply changing a single, seemingly non-critical word in a task description, 
has significant effects on worker's resonses.  Perhaps more importantly, the 
framing treatments were included to provide a reasonable basis for comparison,
and it is clear from our results that the prior tasks performed by a 
worker are much stranger than the effects induced by descriptions of a task's
purpose, or the requester's mandate.

>>>>

\begin{mydef}
	\label{def:bias}
	{\upshape Maximum Bias:}
	Let $\mathcal{D}$ be a binary decision function, which takes a 
	work-product
	$r \in P \cup Q$ as input, and outputs a bit $\mathcal{D}(r)=b$, where 
	$b \in \{0,1\}$. Denote the \emph{bias} of $\mathcal{D}$, due to the
	different priming of $\mathcal{P}$ and $\mathcal{Q}$ by
	$\theta_\mathcal{D}(P,Q)$ and define it to be the difference 
	in the expected output of $\mathcal{D}$ when acting on work-products from 
	$P$ and $Q$:
	$$
	\theta_\mathcal{D}(\mathcal{P},\mathcal{Q}) = 
		\left| 
			\mathrm{E}\left\{ \mathcal{D}(P) \right\} 
			- \mathrm{E}\left\{ \mathcal{D}(Q) \right\} 
		\right|,
	$$
	where $p \in P$, $q \in Q$.  Then, define the difference in priming 
	between $\mathcal{P}$ and $\mathcal{Q}$ to be the worst-case bias, i.e. 
	the bias of the most susceptible decision:
	$$
	\theta(\mathcal{P},\mathcal{Q}) = 
		\sup_\mathcal{D} \theta_\mathcal{D}(P,Q)
	$$
\end{mydef}
If $\mathcal{D}$ is the condition of an \texttt{if}-statement, then the 
definition above is the change in the fraction of the time that a given 
path of execution is followed due to HPU priming.

@@

\paragraph{Sufficiency of framing.} Given just how much stronger
inter-task effects were, the reader may wonder whether the framing was 
in some sense ``sufficient''.  
We designed our framing tasks based on
work that had previously studied framing effects in micro-task settings.  
Prior studies have shown that framing the purpose of a task, or indeed, 
simply changing a single, seemingly non-critical word in a task description, 
has significant effects on worker's resonses \cite{thibodeau2013natural}.  Perhaps more importantly, the 
framing treatments were included to provide a reasonable basis for comparison,
and it is clear from our results that the prior tasks performed by a 
worker are much stranger than the effects induced by descriptions of a task's
purpose, or the requester's mandate.
